Single Bivalent Level Analysis

### 2020-01-28 doc/Bivalent_Analysis.Rmd
in the middle of work and ideas

setwd("~./MLH1repo/")
#load Clean BivData
load(file="data/CleanBivData_1.27.20.RData")

@@

Brief lit review for SC length and MLH1 expections.

```{r show.SC.length, echo=FALSE}
#for now remove the 
#Curated_BivData.99 <- Curated_BivData[Curated_BivData$hand.foci.count #<5,]
#CHECK THAT THE ABOVE TOO MANY FOCI BIVALENTS DON"T EXSIS

@@

SC.lengths.1CO <- ggplot(Curated_BivData[Curated_BivData$hand.foci.count == 1,], aes(y = chromosomeLength, x=strain, fill=sex, color=strain))+geom_boxplot(aes(alpha=0.5))+geom_jitter(aes(alpha=0.2))+  ggtitle("1COs male and females") +ylim(c(30,250))+scale_color_manual(values=colors_of_strains)

@@

#nested boxplots
SC.length_Nested_boxplots <- ggplot(Curated_BivData99, aes(y = chromosomeLength, x=strain, fill=as.factor(hand.foci.count) ))+geom_boxplot(aes(alpha=0.5))+ggtitle("SC Lengths by Chrm Class")+facet_wrap(subsp~sex, scales="free")+ylim(c(25,255))
SC.length_Nested_boxplots

#+ +geom_jitter(aes(alpha=0.2))

In the plot above the SC length ~ higher hand foci cells. Any of the chromosome classes above 3, that don't have a higher mean -- are likely due to low data number.

First draft of the SC length plot. I'd like to add the hand foci count to the x axis.
(also add the PWD - male data)

TRY ADDING NESTED box plots for hand.foci.count

#### Mixed Model Tests

@@

@@

```{r MM_2_SC.length_2_DELETE, echo=FALSE, eval=FALSE}
#Long_biv_mouse.avs_4MM
#as.data.frame( round(  summary(BivData.MixedModel.HQ)$tTable, 6 ) )

@@

@@

@@

ToDo: make a melt.DF with the IFD1, IFD2, IFD3 in a single cols

explain the difference between the raw and PER measures. Why should I use /examine the IFD.PER?

@@

@@

<!-- 
# old drafts

>>>>

setwd("~./MLH1repo/")
#load Clean BivData
load(file="data/CleanBivData_1.28.20.RData")

@@

<!--Brief lit review for SC length and MLH1 expections. -->

We expect female SC lengths to be longer (refs).

In the plot above the SC length ~ higher hand foci cells. Any of the chromosome classes above 3, that don't have a higher mean are likely due to low data number.

```{r show.SC.length, echo=FALSE, warning=FALSE}
#for now remove the 
#Curated_BivData.99 <- Curated_BivData[Curated_BivData$hand.foci.count #<5,]
#CHECK THAT THE ABOVE TOO MANY FOCI BIVALENTS DON"T EXSIS

@@

#SC.lengths.1CO <- ggplot(Curated_BivData[Curated_BivData$hand.foci.count == 1,], aes(y = chromosomeLength, x=strain, fill=sex, color=strain))+geom_boxplot(aes(alpha=0.5))+geom_jitter(aes(alpha=0.2))+  ggtitle("1COs male and females") +ylim(c(30,250))+scale_color_manual(values=colors_of_strains)

@@

#nested boxplots
SC.length_Nested_boxplots <- ggplot(Curated_BivData99, aes(y = chromosomeLength, x=strain, fill=as.factor(hand.foci.count) ))+geom_boxplot(aes(alpha=0.5))+ggtitle("SC Lengths by Chrm Class")+facet_wrap(subsp~sex, scales="free")+ylim(c(25,255))

SC.length_Nested_boxplots

#+ +geom_jitter(aes(alpha=0.2))
```

The dependant variables I'll be testing in the mixed model framework are:

- Pooled SC lengths

- 1CO

- 2CO

- 3CO

- long.biv

### Mixed Model Tests

@@

#### Pooled SC Lengths

@@

```{r MM_2_SC.length_2_DELETE, echo=FALSE, eval=FALSE}
#review this block!!

#Long_biv_mouse.avs_4MM
#as.data.frame( round(  summary(BivData.MixedModel.HQ)$tTable, 6 ) )

@@

#### 1CO

Insert the results for the MMs using the dependant variable 1CO

#### 2CO

#### 3CO

#### long.biv

## Strain Comparisons

Dive deeper into the sex specific pattern for each strain.  (I think for all the within strain comparisons across sexes the general pattern is met of females being longer)

```{r WSB, echo=FALSE}
#make the dataset
WSB.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "WSB",]
#correct and remove, 26dec17_18nov17_WSB_f4_sp1_12_rev_28, 26dec17_18nov17_WSB_f4_sp1_12_rev_27
table(WSB.Bivalents.DF$sex, WSB.Bivalents.DF$hand.foci.count)

#plot the differences
wsb.ploty <- ggplot(WSB.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()
wsb.ploty

#make a table of the means and n ect
wsb.table <- ddply(WSB.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test
wsb.ttest  <- t.test(WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "female"], WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "male"])

@@

```{r LEW, echo=FALSE}
#make the dataset
LEW.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "LEW",]
table(LEW.Bivalents.DF$sex, LEW.Bivalents.DF$hand.foci.count)

#plot the differences
LEW.ploty <- ggplot(LEW.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

LEW.ploty
#remove the NAs

#make a table of the means and n ect
LEW.table <- ddply(LEW.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
LEW.ttest  <- t.test(LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "female"], LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "male"])

```{r G, echo=FALSE}
#make the dataset
G.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "G",]
table(G.Bivalents.DF$sex, G.Bivalents.DF$hand.foci.count)

#plot the differences
G.ploty <- ggplot(G.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

G.ploty
#remove the NAs

#make a table of the means and n ect
G.table <- ddply(G.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
G.ttest  <- t.test(G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "female"], G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "male"])

```{r PWD, echo=FALSE}
#make the dataset
PWD.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "PWD",]
table(PWD.Bivalents.DF$sex, PWD.Bivalents.DF$hand.foci.count)

#plot the differences
PWD.ploty <- ggplot(PWD.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

PWD.ploty
#remove the NAs

#make a table of the means and n ect
PWD.table <- ddply(PWD.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
PWD.ttest  <- t.test(PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "female"], PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "male"])

```{r KAZ, echo=FALSE}
#make the dataset
KAZ.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "KAZ",]
table(KAZ.Bivalents.DF$sex, KAZ.Bivalents.DF$hand.foci.count)

#plot the differences
KAZ.ploty <- ggplot(KAZ.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

KAZ.ploty
#remove the NAs

#make a table of the means and n ect
KAZ.table <- ddply(KAZ.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
KAZ.ttest  <- t.test(KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "female"], KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "male"])

```{r SKIVE, echo=FALSE}
#make the dataset
SKIVE.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "SKIVE",]
table(SKIVE.Bivalents.DF$sex, SKIVE.Bivalents.DF$hand.foci.count)

#plot the differences
SKIVE.ploty <- ggplot(SKIVE.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

SKIVE.ploty
#remove the NAs

#make a table of the means and n ect
SKIVE.table <- ddply(SKIVE.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
SKIVE.ttest  <- t.test(SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "female"], SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "male"])

```{r MSM, echo=FALSE}
#make the dataset
MSM.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MSM",]
table(MSM.Bivalents.DF$sex, MSM.Bivalents.DF$hand.foci.count)

#plot the differences
MSM.ploty <- ggplot(MSM.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MSM.ploty
#remove the NAs

#make a table of the means and n ect
MSM.table <- ddply(MSM.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MSM.ttest  <- t.test(MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "female"], MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "male"])

```{r MOLF, eval=FALSE}
#make the dataset
MOLF.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MOLF",]
table(MOLF.Bivalents.DF$sex, MOLF.Bivalents.DF$hand.foci.count)

#plot the differences
MOLF.ploty <- ggplot(MOLF.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MOLF.ploty
#remove the NAs

#make a table of the means and n ect
MOLF.table <- ddply(MOLF.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MOLF.ttest  <- t.test(MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "female"], MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "male"])

### Summary

@@

<!--
ToDo: make a melt.DF with the IFD1, IFD2, IFD3 in a single cols

explain the difference between the raw and PER measures. Why should I use /examine the IFD.PER?
-->

@@

## Strain Comparisons

Dive deeper into the sex specific pattern for each strain.

```{r WSB.IFD, echo=FALSE}
#make the dataset
#WSB.Bivalents.DF

table(WSB.Bivalents.DF$sex, WSB.Bivalents.DF$hand.foci.count)#the 2CO's will be used

#plot the differences
wsb.ploty_IFD <- ggplot(WSB.Bivalents.DF[WSB.Bivalents.DF$hand.foci.count == 2,],  aes(y=IFD1_ABS, x = sex, color= as.factor(mouse)))+geom_jitter()+ggtitle("")
wsb.ploty_IFD

#try plotting the other IFD

#make a table of the means and n ect
wsb.table_IFD <- ddply(WSB.Bivalents.DF, c("sex"), summarise,

                       mean_SC = mean(chromosomeLength),
                       n_SC = length(Obj.ID),

                  mean.IFD_2CO = mean(IFD1_ABS[which(hand.foci.count == 2)], na.rm = TRUE),
                  mean.IFD.PER = mean(IFD1_PER[which(hand.foci.count == 2)], na.rm = TRUE),

                  n_2CO =  sum(hand.foci.count == 2, na.rm = TRUE) #this is the right syntax
)

#can I plot these stats?

#run a t.test
wsb.ttest  <- t.test(WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "female"], WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "male"])

```{r LEW.IFD, echo=FALSE}
#make the dataset
LEW.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "LEW",]
table(LEW.Bivalents.DF$sex, LEW.Bivalents.DF$hand.foci.count)

#plot the differences
LEW.ploty <- ggplot(LEW.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

LEW.ploty
#remove the NAs

#make a table of the means and n ect
LEW.table <- ddply(LEW.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
LEW.ttest  <- t.test(LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "female"], LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "male"])

```{r G.IFD, echo=FALSE}
#make the dataset
G.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "G",]
table(G.Bivalents.DF$sex, G.Bivalents.DF$hand.foci.count)

#plot the differences
G.ploty <- ggplot(G.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

G.ploty
#remove the NAs

#make a table of the means and n ect
G.table <- ddply(G.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
G.ttest  <- t.test(G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "female"], G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "male"])

```{r PWD.IFD, echo=FALSE}
#make the dataset
PWD.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "PWD",]
table(PWD.Bivalents.DF$sex, PWD.Bivalents.DF$hand.foci.count)

#plot the differences
PWD.ploty <- ggplot(PWD.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

PWD.ploty
#remove the NAs

#make a table of the means and n ect
PWD.table <- ddply(PWD.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
PWD.ttest  <- t.test(PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "female"], PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "male"])

```{r KAZ.IFD, echo=FALSE}
#make the dataset
KAZ.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "KAZ",]
table(KAZ.Bivalents.DF$sex, KAZ.Bivalents.DF$hand.foci.count)

#plot the differences
KAZ.ploty <- ggplot(KAZ.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

KAZ.ploty
#remove the NAs

#make a table of the means and n ect
KAZ.table <- ddply(KAZ.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
KAZ.ttest  <- t.test(KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "female"], KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "male"])

```{r SKIVE.IFD, echo=FALSE}
#make the dataset
SKIVE.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "SKIVE",]
table(SKIVE.Bivalents.DF$sex, SKIVE.Bivalents.DF$hand.foci.count)

#plot the differences
SKIVE.ploty <- ggplot(SKIVE.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

SKIVE.ploty
#remove the NAs

#make a table of the means and n ect
SKIVE.table <- ddply(SKIVE.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
SKIVE.ttest  <- t.test(SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "female"], SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "male"])

```{r MSM.IFD, echo=FALSE}
#make the dataset
MSM.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MSM",]
table(MSM.Bivalents.DF$sex, MSM.Bivalents.DF$hand.foci.count)

#plot the differences
MSM.ploty <- ggplot(MSM.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MSM.ploty
#remove the NAs

#make a table of the means and n ect
MSM.table <- ddply(MSM.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MSM.ttest  <- t.test(MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "female"], MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "male"])

```{r MOLF.IFD, eval=FALSE}
#make the dataset
MOLF.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MOLF",]
table(MOLF.Bivalents.DF$sex, MOLF.Bivalents.DF$hand.foci.count)

#plot the differences
MOLF.ploty <- ggplot(MOLF.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MOLF.ploty
#remove the NAs

#make a table of the means and n ect
MOLF.table <- ddply(MOLF.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum(which(hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum(which(hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum(which(hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum(which(hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MOLF.ttest  <- t.test(MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "female"], MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "male"])

@@

<!-- 
# old drafts / trash pile
